divan: An R Shiny app for exploratory functional diversity analyses

### 2023-11-02 paper/paper.Rmd
update

---
title: 'divan: An R Shiny app for exploratory functional diversity analyses'
author:
  - name: Facundo X. Palacio
    affiliation: "1, 2"
    corresponding: true
  - name: Caio Graco-Roza
    affiliation: 3
  - name: Emma J. Hudgins
    affiliation: 4
affiliation:
  - name: Sección Ornitología, Universidad Nacional de La Plata, B1900FWA La Plata, Argentina
    index: 1
  - name: Consejo Nacional de Investigaciones Científicas y Técnicas, La Plata, Argentina
    index: 2
  - name: University of Helsinki, Helsinki, Finland
    index: 3
  - name: School of Agriculture, Food, and Ecosystem Sciences, The University of Melbourne, Parkvile 3010 VIC, Australia
    index: 4
date: "`r format(Sys.time(), '%d %B %Y')`"
bibliography: paper.bib
---

@@

![Figure 1. The graphical user interface (GUI) of **divan** after loading a community matrix. (a) Sidebar menu, (b) heatmap plus dendrogram of the community matrix, (c) rarefaction curves of individual sites.". \label{fig:fig1}](../fig/fig_1.jpg)

>>>>

---
title: 'divan: An R Shiny app for exploratory functional diversity analyses'
author:
- name: Facundo X. Palacio
  affiliation: 1, 2
  corresponding: yes
- name: "Caio Graco-Roza"
  affiliation: 3
- name: Emma J. Hudgins
  affiliation: 4
date: "2 November 2023"
affiliation:
- name: Sección Ornitología, Universidad Nacional de La Plata, Argentina
  index: 1
- name: Consejo Nacional de Investigaciones Científicas y Técnicas, Argentina
- index: 2
- name: University of Helsinki, Helsinki, Finland
  index: 3
- name: School of Agriculture, Food, and Ecosystem Sciences, The University of Melbourne,
    Australia
  index: 4
tags:
- Shiny
- functional ecology
- biodiversity
- functional traits
bibliography: paper.bib
output: md_document
---

@@

![Figure 1. The graphical user interface (GUI) of **divan** after loading a community matrix. (a) Sidebar menu, (b) heatmap plus dendrogram of the community matrix, (c) rarefaction curves of individual sites. \label{fig:fig1}](../fig/fig_1.jpg)
